\emph{Cree}: A modern toolbox for readymade economic experiments

### 2015-06-06 Latex/paper.tex
Fixed grammar and spelling

\Cree is build using web technologies. Content is structured using the markup language \emph{HTML}. The layout and presentation across different screen sizes is archived with the style sheet language \emph{CSS}. And all logic is constructed using the programming language \emph{JavaScript}. All web browsers interpret these three cornerstone languages and render pages accordingly. Subjects participate in \Cree experiments though a web browser. Because \Cree is fundamentally native to the web browser, it avoids many of the restrictions, that other toolboxes suffer from.

@@

While this paper deals with internet experiments in general, it continuously refer to studies that use subjects from Amazon's \emph{Mechanical Turk}. This is not to highlight or promote the use of \emph{Mechanical Turk}, it is simply because the bulk of internet experiments use this system.

@@

\Cree requires a server, ie. any computer with \emph{Node.js} installed. \Cree has several dependencies -- because it is built on general-purpose software libraries -- however all of these dependencies are automatically installed, or come pre-bundled, with \Cree. The server will need to be connected to the devices used by the subject, either through the internet or through a local network (eg. WiFi).

@@

Subjects access \Cree experiments though an web browser. Any modern web browser will suffice\footnotemark[1], which means that subjects can participate in experiments using smart-phones, tablets, or any computer (Windows, Mac, Linux). Every subject will need a device. The researcher can choose to provide devices, or have subjects use their own personal devices.

@@

\emph{z-Tree} is currently the commonly used toolbox for conducting economic experiments. The development of \emph{z-Tree} started in 1995 and has been updated continuously \citep{Fischbacher_2007}. However the foundation and guiding principles of \emph{z-Tree} is based on the technology that was available two decades ago. Several other toolboxes exist that can run economic experiments. Below I divide the the toolboxes into four categories based on the restrictions they place on the equipment facing subjects:

@@

Toolboxes, such as \emph{z-Tree}, are applications. They are written for a specific operating system, and will only run on that specific operating system. All toolboxes in this category requires Microsoft Windows. These applications are not easily ported to other computer operating systems. And they will require a complete restructuring -- focused on optimising screen sizes and battery life -- if they are ever to run on smart-phones or tablets. In addition, applications will have to be downloaded (and installed) on the computer facing subjects, before they can participate in experiments. This requirement hinders subjects from using their personal devices.

The second category contains toolboxes written in \emph{Python}. Python is platform independent, so these toolboxes can run on several operating systems, but they require that Python is installed on the equipment facing subjects\footnotemark[2]. These toolboxes also require downloading software.

@@

\begin{enumerate}
\item subjects have experience from related experiments. By pooling 16,408 observations (or completed tasks) across 132 studies, they find just 7,498 unique subjects -- averaging 2.24 observation per subject. The 10\% most prolific subjects account for 41\% of all observations. In addition \cite{Chandler_Mueller_Paolacci_2014} survey 300 workers on \emph{Mechanical Turk} and find that 56\% have previously been exposed to the \emph{Prisoner's dilemma} and 52\% to the \emph{Ultimatum game}. 
\item subjects share information about experiments. About one fourth of workers in the \cite{Chandler_Mueller_Paolacci_2014} survey respectively report they know other workers in person, and that they read or discuss \emph{Mechanical Turk} online on blogs and forums. The focus of the conversation is typically not the specific contents of the experiment, but rather pay rates and reputation. \cite{Chandler_Mueller_Paolacci_2014} conclude that researchers should be particularly aware of cross talk, when information can increase financial rewards -- such as when using techniques to increase attention (\emph{instructional manipulation checks}, or \emph{got-cha} questions), or when using techniques to deny payment. They suggest that researchers asks subjects how they found the experiment, and monitor discussion boards that refer a lot of subjects to the experiment.
\item few subjects attempt to participate repeatedly in the same experiment. Amazon forbids multiply or \emph{sock-puppet} accounts, and actively enforces this policy. \cite{Chandler_Mueller_Paolacci_2014} find 1.2\% of subjects share IP addresses as well as demographic characteristics -- eg. possible \emph{sock-puppet} accounts. They attribute the low percentage to the active enforcement by Amazon.
\end{enumerate}

@@

\Cree does not include a prescreening system to manage the pool of subjects, so recruitment is handled manually by the researcher. The selection process is crucial, and researchers should carefully consider the degree to which subjects can self-select into experiments, since this may invalidate the underlying assumption of naïve subjects. \Cree automatically logs referrals from other websites. And researchers can restrict \Cree so it only accepts one subject per IP address, creating additional protection against subjects participating multiple times in the same experimental session.

@@

When the researcher initiates the experiment, \Cree returns the URL addresses, that subjects use to join the experiment. Two URLs are displayed, since subjects can participate over the internet and through the local network. URLs should be distributed accordingly. The researcher distributes the URL to participants (via printed hand-outs, e-mail, third-party recruitment system, etc). Subjects join the experiment simply by clicking a link, or by typing the URL into their web browser. \Cree automatically tests if the server can connect to the internet, if this fails then \Cree only displays the local network URL\footnotemark[5].

@@

Besides recruitment and distribution of addresses, there is coordination. In experiments where subjects interact with each other in real-time, the researcher must coordinate subjects so they start the experiment simultaneously. The researcher can specify that \Cree should wait for sufficiently many subjects to join, before starting the session. Ie. the first subject joining will be put on hold, until the last required subject joins. Subjects have limited patience, so the researcher needs to coordinate subjects on a very narrow interval of only a few minutes. There are a couple of different approaches that the researcher can take here. In laboratory experiments it is common to invite more participants than needed for a given session (due to ``no shows''). This option is also possible in \Cree, since \Cree turns down subjects once a session is filled. There is a semi-continuous option that expands the interval. For instance in the \emph{Prisoner's dilemma} it is common with only two subjects interacting with each other. So instead of waiting for all subjects to join the session, the semi-continuous option will start whenever two new subjects join. However with this option the researcher loses the ability to randomise subjects, ie. pair a subject with another. The lack of randomisation may lead to reciprocity among subjects. There is a third fully-continuous option, where the server simply restarts the experiment after each session. This option can be used in conjunction with fewer subjects per session. If subjects show up late for the first session, they wait for the session to end, whereafter they can join the second session, and so on. All of this continues until the researcher manually stops the experiment.

@@

A main priority for researchers is that the software they use to run experiments is stable. Crashes are not only costly and time consuming, but also detrimental to the researcher's reputation among the participating subjects.

@@

If subjects attempt to abort the experiment untimely, \Cree displays a warning message. The occurrence of these warning messages are logged. In addition \Cree logs when the subject's web browsers is out of focus\footnotemark[7] -- this is a proxy measure for inattention. The figure below plots the session of one subject. The figure includes connection, disconnection, the stages of the experiment, and periods of inattention (areas shaded red). The full lines mark the beginning of a new stage. The dotted lines are where the subject waits for the other participant.

@@

In sum the researcher needs to carefully consider the selection process, to ensure that subjects are representative and that results have general validity. When subjects ability to self-select into experiments is restricted, it remains unclear if subjects will participate in hour-long experiments, and it is unclear how attentive they are during these long unsupervised sessions.

There are two alternative approaches, regarding time and duration, that the researchers might consider when designing the experiment. One is the approach of \citet*{Pettit_Friedman_Kephart_Oprea_2014} which speeds up the adjustment process by allowing subjects to continuously change and adapt strategies. They refer to one study where distinctive, long-term implications are observable in rounds lasting only 120 seconds. The other approach, suggested by \cite{Charness_Gneezy_Kuhn_2013}, is to create long time-series data, ie. by recalling subjects every day, week or month. In a traditional laboratory experiment, this would be time consuming and highly inconvenient for subjects, but less so in extra-laboratory settings such as classrooms or over the internet. \cite[p. 96]{Charness_Gneezy_Kuhn_2013} argue that \emph{``the classic 10–20 period repetition of the public-goods game may not be a good analog for the expression of preference for tax policy that citizens make when they vote every couple of years''}. \Cree can execute both alternative approaches, since it allows real-time interaction among subjects and works in \emph{extra-laboratory} settings.

@@

For in-person experiments the researcher can pay subjects in cash. For experiments conducted over the internet payment will require a third-party payment provider. This could be national provides, such as the danish \emph{MobilePay} or \emph{Swipp}. Or it could be international providers such as \emph{PayPal}. When a third-party payment provider is used, subjects will enter their mobile phone number, email address, or receive a voucher code they can use to claim their payment. At the end of every session \Cree generates a list with the payment for every subject, and with the respective payment method and transfer details.

@@

Discouraging cheating in unsupervised experiments is difficult. And additional considerations are needed since subjects participate in experiments using a web browser. First, \cite{Goodman_Cryder_Cheema_2013} have shown that \emph{Mechanical Turk} subjects search for the correct answers to factual questions on the internet. Subjects look up answers, even when payment is independent of answering correctly. And when subjects are paid for the correct answer, they are more likely to look up the answer. Asking subjects not to use any externals sources reduces the number of subjects that look up the answer, but it does not completely eliminate cheating. Secondly, toolboxes that are native to the web browser are at a disadvantage compared to the toolboxes in the three other categories (discussed in section~\ref{SS:Alternatives}), since pages are rendered in the subject's web browser. Thus the source code to the unrendered pages is easily viewable and relatively easy to manipulate \citep[25m. 12s.]{Hawkes_2011}. In \Cree Subjects cannot cheat by manipulating how the page is rendered, since the server has final authority and controls the experiment. But subjects may attempt to cheat by sending false or manipulated inputs back to the server. It is therefore crucial, when the researcher designs the experiment, that all inputs are validated on the server. In addition since the source code of the page is accessible, it should not contain information that disclose the purpose of the experiment, the treatment, nor optimal strategies -- eg. instead of using variables names such as \texttt{Option\_Nash\_Equilibrium} and \texttt{Option\_Sub\_Optimal}, the researcher should use generic names such as \texttt{OptionX} and \texttt{OptionY}. A third issue is coercion among subjects. Coercion may arise in unsupervised in-person experiments where subjects are seated closely (ie. classrooms, work places, etc.), or in internet experiments where subjects are able to self-select into the experiment, and therefore invite others to join with the aim of manipulating the experiment. In \Cree the researcher can randomise subjects across groups, roles and treatments, but other than this \Cree cannot alleviate coercion. If possible it is recommended that in-person experiments are supervised. And researchers should limit the subject's ability to self-select into the experiment, when conducting experiments over the internet.

@@

This short walkthrough indicates that the behaviour observed in laboratories for most part also holds outside of the laboratory. But perhaps not in other cultures, or with extremely high payouts (such as rural India). Similarly social preferences differ when subjects self-identify with a community (the gamers). And the researcher should be particularly observant of the selection process when conducting experiments on risk or time preferences, since both age and circumstances will affect experimental results.

@@

There is yet no research on how or if results are influenced by the devices used by subjects in experiments. \Cree records the type of device used by subjects, as well as the screen size. The researcher can use this to post hoc control for differences in the results. Alternatively the researcher can a priori exclude specific devices from participating in the experiment. This may be particular useful in experiments where the subject's reaction time is critical (such as experiments on auctions). I expect that subjects using smart-phones react slower, than subjects on other types of devices. In part due to lower processing power and screen size, but also due to the different input method. The screen, keyboard and mouse are separated on a computer, while on a smart-phone the mouse and keyboard are built into a screen, that only covers about one-fourteenth of the area of a computer screen. Subjects with a smart-phone would be at a disadvantage when entering text or numbers repetitively and at length, or when constantly having to switch between keyboard and pointing. Another alternative is levering the playing field, by using similar input method across all devices. \cite{Choi_Fisman_Gale_Kariv_2007} proposed using a graphical interface. For instance, if the subject is asked to allocate an amount to consumption out of a budget of \$100. Then instead of entering this amount into a form, there is a line graphically representing the \$100 budget, and the subject simply clicks accordingly on the line to input his or her allocation. Similar method has also been implemented by \cite{Pettit_Friedman_Kephart_Oprea_2014} in the \emph{ConG} toolbox. \Cree leverages the JavaScript library \emph{D3.js} to build graphics.

@@

There are some misconception that I would like to address. 
\begin{enumerate}
\item The main purpose of a toolbox is not to offer comfort or convenience to researchers, but to offer the necessary tools. Convenience is secondary.
\item There is a trade-off between usability and flexibility. Every improvement in usability is based on a judgement call by the programmer. Usability is improved when the set of possible choices are reduced, this in turn reduces flexibility. Thus a toolbox should be evaluated on its ability to balance the trade-off between usability and flexibility. 
\item All toolboxes essentially require some programming skills. It is true that some toolboxes allow researchers to run preprogrammed experiments, without any additional programming. But once the researcher starts building own experiments, or significantly modifies existing experiments, programming is unavoidable. A programming language is nothing more than human logic and instructions in a machine interpretable format, and this is why programming is unavoidable when researchers build logic into their experiments.
\end{enumerate}

The guiding principle behind \Cree is to offer a solid and highly flexible foundation, that gives researchers the necessary tools to carry out their research, irrespective of location and available devices. The current version of \Cree does require some programming skills. An interface -- providing convenience when running preprogrammed experiments and when implementing minor changes -- could be added on top of this foundation in a future version. The interface would be a supplement. But with the foundation in order, this would not be at the expense of the general flexibility of \Cree. \Cree relies on JavaScript to build logic into experiments. Because JavaScript is a general-purpose programming language and widely used, many of the procedures necessary to build more complex experiments are already easily available. Thereby avoiding the trap noted by \citet[p. 177]{Fischbacher_2007} when discussing the current limitations of \emph{z-tree}; \emph{``there are situations in which programming is unnecessarily complicated, since z-Tree neither knows procedures nor complex data types ... One of the planned future steps in the development of z-Tree is thus an extension of the programming language to make programming of more complex experiments easier''}. \Cree uses the CSS framework \emph{Bootstrap}, which insures that pages scale seamlessly across small and big screens. In addition it ensures that pages look identical across different browsers and devices, for given screen sizes. Since Bootstrap handles all this, knowledge of CSS is not need to build elegant experiments that have a consistent look across devices. Some knowledge of HTML is  helpful, but not required since the researcher can use third-party drag and drop tools such as \emph{LayoutIt!} or \emph{Jetstrap} to build pages that work with \emph{Bootstrap}\footnotemark[8].

>>>>

\Cree is build using web technologies. Content is structured using the markup language \emph{HTML}. The layout and presentation across different screen sizes is archived with the style sheet language \emph{CSS}. And all logic is constructed using the programming language \emph{JavaScript}. All web browsers interpret these three cornerstone languages and render pages accordingly. Subjects participate in \Cree experiments though a web browser. Because \Cree is fundamentally native to the web browser, it avoids many of the restrictions that other toolboxes suffer from.

@@

While this paper deals with internet experiments in general, it continuously refers to studies that use subjects from Amazon's \emph{Mechanical Turk}. This is not to highlight or promote the use of \emph{Mechanical Turk}, it is simply because the bulk of internet experiments use this system.

@@

\Cree requires a server, ie. any computer with \emph{Node.js} installed. \Cree has several dependencies -- because it is built on general-purpose software libraries -- however all of these dependencies are automatically installed, or come pre-bundled, with \Cree. The server will need to be connected to the devices used by the subject, either through the internet or through a local network (eg. Wi-Fi).

@@

Subjects access \Cree experiments though a web browser. Any modern web browser will suffice\footnotemark[1], which means that subjects can participate in experiments using smart-phones, tablets, or any computer (Windows, Mac, Linux). Every subject will need a device. The researcher can choose to provide devices, or have subjects use their own personal devices.

@@

\emph{z-Tree} is currently the commonly used toolbox for conducting economic experiments. The development of \emph{z-Tree} started in 1995 and has been updated continuously \citep{Fischbacher_2007}. However the foundation and guiding principles of \emph{z-Tree} is based on the technology that was available two decades ago. Several other toolboxes exist that can run economic experiments. Below I divide the toolboxes into four categories based on the restrictions they place on the equipment facing subjects:

@@

Toolboxes, such as \emph{z-Tree}, are applications. They are written for a specific operating system, and will only run on that specific operating system. All toolboxes in this category require Microsoft Windows. These applications are not easily ported to other computer operating systems. And they will require a complete restructuring -- focused on optimising screen sizes and battery life -- if they are ever to run on smart-phones or tablets. In addition, applications will have to be downloaded (and installed) on the computer facing subjects, before they can participate in experiments. This requirement hinders subjects from using their personal devices.

The second category contains toolboxes written in \emph{Python}. Python is platform independent, so these toolboxes can run on several operating systems, but they require that Python be installed on the equipment facing subjects\footnotemark[2]. These toolboxes also require downloading software.

@@

\begin{enumerate}
\item subjects have experience from related experiments. By pooling 16,408 observations (or completed tasks) across 132 studies, they find just 7,498 unique subjects -- averaging 2.24 observation per subject. The 10\% most prolific subjects account for 41\% of all observations. In addition \cite{Chandler_Mueller_Paolacci_2014} survey 300 workers on \emph{Mechanical Turk} and find that 56\% have previously been exposed to the \emph{Prisoner's dilemma} and 52\% to the \emph{Ultimatum game}. 
\item subjects share information about experiments. About one fourth of workers in the \cite{Chandler_Mueller_Paolacci_2014} survey respectively report they know other workers in person, and that they read or discuss \emph{Mechanical Turk} online on blogs and forums. The focus of the conversation is typically not the specific contents of the experiment, but rather pay rates and reputation. \cite{Chandler_Mueller_Paolacci_2014} conclude that researchers should be particularly aware of cross talk, when information can increase financial rewards -- such as when using techniques to increase attention (\emph{instructional manipulation checks}, or \emph{got-cha} questions), or when using techniques to deny payment. They suggest that researchers ask subjects how they found the experiment, and monitor discussion boards that refer a lot of subjects to the experiment.
\item few subjects attempt to participate repeatedly in the same experiment. Amazon forbids multiply or \emph{sock-puppet} accounts, and actively enforces this policy. \cite{Chandler_Mueller_Paolacci_2014} find 1.2\% of subjects share IP addresses as well as demographic characteristics -- eg. possible \emph{sock-puppet} accounts. They attribute the low percentage to the active enforcement by Amazon.
\end{enumerate}

@@

\Cree does not include a prescreening system to manage the pool of subjects, so the researcher handles recruitment manually. The selection process is crucial, and researchers should carefully consider the degree to which subjects can self-select into experiments, since this may invalidate the underlying assumption of naïve subjects. \Cree automatically logs referrals from other websites. And researchers can restrict \Cree so it only accepts one subject per IP address, creating additional protection against subjects participating multiple times in the same experimental session.

@@

When the researcher initiates the experiment, \Cree returns the URL addresses that subjects use to join the experiment. Two URLs are displayed, since subjects can participate over the internet and through the local network. URLs should be distributed accordingly. The researcher distributes the URL to participants (via printed hand-outs, e-mail, third-party recruitment system, etc). Subjects join the experiment simply by clicking a link, or by typing the URL into their web browser. \Cree automatically tests if the server can connect to the internet, if this fails then \Cree only displays the local network URL\footnotemark[5].

@@

Besides recruitment and distribution of addresses, there is coordination. In experiments where subjects interact with each other in real-time, the researcher must coordinate subjects so they start the experiment simultaneously. The researcher can specify that \Cree should wait for sufficiently many subjects to join, before starting the session. Ie. the first subject joining will be put on hold, until the last required subject joins. Subjects have limited patience, so the researcher needs to coordinate subjects on a very narrow interval of only a few minutes. There are a couple of different approaches that the researcher can take here. In laboratory experiments it is common to invite more participants than needed for a given session (due to ``no shows''). This option is also possible in \Cree, since \Cree turns down subjects once a session is filled. There is a semi-continuous option that expands the interval. For instance in the \emph{Prisoner's dilemma} it is common with only two subjects interacting with each other. So instead of waiting for all subjects to join the session, the semi-continuous option will start whenever two new subjects join. However with this option the researcher loses the ability to randomise subjects, ie. pair a subject with another. The lack of randomisation may lead to reciprocity among subjects. There is a third fully-continuous option, where the server simply restarts the experiment after each session. This option can be used in conjunction with fewer subjects per session. If subjects show up late for the first session, they wait for the session to end, hereafter they can join the second session, and so on. All of this continues until the researcher manually stops the experiment.

@@

A main priority for researchers is that the software they use to run experiments is stable. In addition to being costly and time consuming, crashes are also detrimental to the researcher's reputation among the participating subjects.

@@

If subjects attempt to abort the experiment untimely, \Cree displays a warning message. The occurrences of these warning messages are logged. In addition \Cree logs when the subject's web browser is out of focus\footnotemark[7] -- this is a proxy measure for inattention. The figure below plots the session of one subject. The figure includes connection, disconnection, the stages of the experiment, and periods of inattention (areas shaded red). The full lines mark the beginning of a new stage. The dotted lines are where the subject waits for the other participant.

@@

In sum the researcher needs to carefully consider the selection process, to ensure that subjects are representative and that results have general validity. When subject's ability to self-select into experiments is restricted, it remains unclear if subjects will participate in hour-long experiments, and it is unclear how attentive they are during these long unsupervised sessions.

There are two alternative approaches, regarding time and duration that the researchers might consider when designing the experiment. One is the approach of \citet*{Pettit_Friedman_Kephart_Oprea_2014} which speeds up the adjustment process by allowing subjects to continuously change and adapt strategies. They refer to one study where distinctive, long-term implications are observable in rounds lasting only 120 seconds. The other approach, suggested by \cite{Charness_Gneezy_Kuhn_2013}, is to create long time-series data, ie. by recalling subjects every day, week or month. In a traditional laboratory experiment, this would be time consuming and highly inconvenient for subjects, but less so in extra-laboratory settings such as classrooms or over the internet. \cite[p. 96]{Charness_Gneezy_Kuhn_2013} argue that \emph{``the classic 10–20 period repetition of the public-goods game may not be a good analog for the expression of preference for tax policy that citizens make when they vote every couple of years''}. \Cree can execute both alternative approaches, since it allows real-time interaction among subjects and works in \emph{extra-laboratory} settings.

@@

For in-person experiments the researcher can pay subjects in cash. For experiments conducted over the internet payment will require a third-party payment provider. This could be national provides, such as the Danish \emph{MobilePay} or \emph{Swipp}. Or it could be international providers such as \emph{PayPal}. When a third-party payment provider is used, subjects will enter their mobile phone number, email address, or receive a voucher code they can use to claim their payment. At the end of every session \Cree generates a list with the payment for every subject, and with the respective payment method and transfer details.

@@

Discouraging cheating in unsupervised experiments is difficult. And additional considerations are needed since subjects participate in experiments using a web browser. First, \cite{Goodman_Cryder_Cheema_2013} have shown that \emph{Mechanical Turk} subjects search for the correct answers to factual questions on the internet. Subjects look up answers, even when payment is independent of answering correctly. And when subjects are paid for the correct answer, they are more likely to look up the answer. Asking subjects not to use any externals sources reduces the number of subjects that look up the answer, but it does not completely eliminate cheating. Secondly, toolboxes that are native to the web browser are at a disadvantage compared to the toolboxes in the three other categories (discussed in section~\ref{SS:Alternatives}), since pages are rendered in the subject's web browser. Thus the source code to the unrendered pages is easily viewable and relatively easy to manipulate \citep[25m. 12s.]{Hawkes_2011}. In \Cree Subjects cannot cheat by manipulating how the page is rendered, since the server has final authority and controls the experiment. But subjects may attempt to cheat by sending false or manipulated inputs back to the server. It is therefore crucial, when the researcher designs the experiment, that all inputs are validated on the server. In addition since the source code of the page is accessible, it should not contain information that disclose the purpose of the experiment, the treatment, nor optimal strategies -- eg. instead of using variables names such as \texttt{Option\_Nash\_Equilibrium} and \texttt{Option\_Sub\_Optimal}, the researcher should use generic names such as \texttt{OptionX} and \texttt{OptionY}. A third issue is coercion among subjects. Coercion may arise in unsupervised in-person experiments where subjects are seated closely (ie. classrooms, work places, etc.), or in internet experiments where subjects are able to self-select into the experiment, and therefore invite others to join with the aim of manipulating the experiment. In \Cree the researcher can randomise subjects across groups, roles and treatments, but other than this \Cree cannot alleviate coercion. If possible it is recommended that in-person experiments be supervised. And researchers should limit the subject's ability to self-select into the experiment, when conducting experiments over the internet.

@@

This short walkthrough indicates that the behaviour observed in laboratories for most part also holds outside of the laboratory. Perhaps the results do not hold in other cultures, or with extremely high payouts (such as rural India). Similarly social preferences differ when subjects self-identify with a community (the gamers). And the researcher should be particularly observant of the selection process when conducting experiments on risk or time preferences, since both age and circumstances will affect experimental results.

@@

There is yet no research on how or if results are influenced by the devices used by subjects in experiments. \Cree records the type of device used by subjects, as well as the screen size. The researcher can use this to post hoc control for differences in the results. Alternatively the researcher can a priori exclude specific devices from participating in the experiment. This may be particular useful in experiments where the subject's reaction time is critical (such as experiments on auctions). I expect that subjects using smart-phones react slower, than subjects on other types of devices. In part due to lower processing power and screen size, but also due to the different input method. The screen, keyboard and mouse are separated on a computer, while on a smart-phone the mouse and keyboard are built into a screen that only covers about one-fourteenth of the area of a computer screen. Subjects with a smart-phone would be at a disadvantage when entering text or numbers repetitively and at length, or when constantly having to switch between keyboard and pointing. Another alternative is levering the playing field, by using similar input method across all devices. \cite{Choi_Fisman_Gale_Kariv_2007} proposed using a graphical interface. For instance, if the subject is asked to allocate an amount to consumption out of a budget of \$100. Then instead of entering this amount into a form, there is a line graphically representing the \$100 budget, and the subject simply clicks accordingly on the line to input his or her allocation. Similar method has also been implemented by \cite{Pettit_Friedman_Kephart_Oprea_2014} in the \emph{ConG} toolbox. \Cree leverages the JavaScript library \emph{D3.js} to build graphics.

@@

There are some misconceptions that I would like to address. 
\begin{enumerate}
\item The main purpose of a toolbox is not to offer comfort or convenience to researchers, but to offer the necessary tools. Convenience is secondary.
\item There is a trade-off between usability and flexibility. The programmer bases every improvement in usability on a judgement call. Usability is improved when the set of possible choices are reduced, this in turn reduces flexibility. Thus a toolbox should be evaluated on its ability to balance the trade-off between usability and flexibility. 
\item All toolboxes essentially require some programming skills. It is true that some toolboxes allow researchers to run preprogrammed experiments, without any additional programming. But once the researcher starts building own experiments, or significantly modifies existing experiments, programming is unavoidable. A programming language is nothing more than human logic and instructions in a machine interpretable format, and this is why programming is unavoidable when researchers build logic into their experiments.
\end{enumerate}

The guiding principle behind \Cree is to offer a solid and highly flexible foundation that gives researchers the necessary tools to carry out their research, irrespective of location and available devices. The current version of \Cree does require some programming skills. An interface -- providing convenience when running preprogrammed experiments and when implementing minor changes -- could be added on top of this foundation in a future version. The interface would be a supplement. But with the foundation in order, this would not be at the expense of the general flexibility of \Cree. \Cree relies on JavaScript to build logic into experiments. Because JavaScript is a general-purpose programming language and widely used, many of the procedures necessary to build more complex experiments are already easily available. Thereby avoiding the trap noted by \citet[p. 177]{Fischbacher_2007} when discussing the current limitations of \emph{z-tree}; \emph{``there are situations in which programming is unnecessarily complicated, since z-Tree neither knows procedures nor complex data types ... One of the planned future steps in the development of z-Tree is thus an extension of the programming language to make programming of more complex experiments easier''}. \Cree uses the CSS framework \emph{Bootstrap}, which insures that pages scale seamlessly across small and big screens. In addition it ensures that pages look identical across different browsers and devices, for given screen sizes. Since Bootstrap handles all this, knowledge of CSS is not need to build elegant experiments that have a consistent look across devices. Some knowledge of HTML is  helpful, but not required since the researcher can use third-party drag and drop tools such as \emph{LayoutIt!} or \emph{Jetstrap} to build pages that work with \emph{Bootstrap}\footnotemark[8].
